---
output: github_document
---
# Style your markdown

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/lorenzwalthert/stylermd.svg?branch=master)](https://travis-ci.org/lorenzwalthert/stylermd)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/lorenzwalthert/stylermd?branch=master&svg=true)](https://ci.appveyor.com/project/lorenzwalthert/stylermd)

**Functionality**

This package is simiar to styler, but it styles non-code elements and files
and it does really just one thing: Making every line at most 80 characters. It
supports:

* Both adding and removing linebreaks.
* Files with and without code chunks (any extension).
* Enumerations and bullet list.
* Files with YAML Header.
* Preserves paragraphs.


You can install it from GitHub:
```{r, eval = FALSE}
remotes::install_github("lorenzwalthert/stylermd")
```
**API**

You can use `tidy_text()`, `tidy_file()` and the RStudio Addins (restarting
RStudio after installation). One styles the highlighted text, the other styles 
the active file.

**Example**

```{r, comment = ""}
library(magrittr)
text <- "1. introduced above. We do this by first creating a style guide with the designated wrapper function `create_style_guide()`. It takes transformer"
stylermd::tidy_text(text) %>%
  cat(sep = "\n")
```


