---
output: github_document
---

# Style your markdown

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build
status](https://travis-ci.org/lorenzwalthert/stylermd.svg?branch=master)](https://travis-ci.org/lorenzwalthert/stylermd)
[![AppVeyor build
status](https://ci.appveyor.com/api/projects/status/github/lorenzwalthert/stylermd?branch=master&svg=true)](https://ci.appveyor.com/project/lorenzwalthert/stylermd)

> Just keep up one rule: 80 characters per line. I promise it will take 80% of
your time. -- <cite>Lorenz Walthert</cite>

The main motivation for creating this package was because when working with
bookdown / blogdown or Rmarkdown in general, I spent **way too much time** just
keeping up the 80 character width rule as every word you add or remove in a
paragraph affects all subsequent lines.

**Functionality**

This package is similar to styler, but it styles non-code elements and files and
it does really just one thing: Making every line at most 80 characters, or a
custom line width you can set with the option `stylermd.line_width`, i.e.
`options(stylermd.line_width = 60)`. It supports:

* Both adding and removing line breaks for float text, nested enumerations and 
  bullet lists.
* Files with and without code chunks (any extension).
* Ignoring code chunks and latex equations.
* Files with YAML Header.
* Preserves paragraphs.

You can install it from GitHub:

```{r, eval = FALSE}
remotes::install_github("lorenzwalthert/stylermd")
``` 

**API**

You can use:

* `tidy_text()`.
* `tidy_file()`.
* the RStudio Addins (restarting RStudio after installation). One styles the
  highlighted text, the other styles the active file, remembering the cursor
  position. Set the environment variable `save_after_styling` to `TRUE`, for
  example in your `.Rprofile` to enable saving after styling. Hint: Assign a
  keyboard short-cut for the Addin with *Menu -> Tools -> Modify Keyboard
  Shortcuts* for most productive use.

**Example**

```{r, comment = ""}
library(magrittr)
text <- "1. introduced above. We do this by first creating a style guide with the designated wrapper function `create_style_guide()`. It takes transformer"
stylermd::tidy_text(text) %>%
  cat(sep = "\n")
```

